---
title: "Final Project"
author: "Christopher Loan & Merly Klaas"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rmdHelpers)
library(glue)
source('Scripts/functions.R')
```

```{r}
d0 <- 
  download_clean_data(
    start_year = 2011,
    end_year = 2020
    ) 
```

## In a Shiny app you could have these listed in checkboxes or dropdown lists.
```{r}
## example of selected groups
groups <- 
  c('ALL Students', 
    'Economically Disadvantaged', 
    'Black',
    'White',
    'Not Economically Disadvantaged',
    'Students With Disability', 
    'Students Without Disability'#,'Kindergarteners' # add this to trigger warning
  )
```

```{r}
test <- grad_year_plots(
  cleaned_data_frame = d0, 
  groups_of_interest = groups
  )
```

# Still need to do this: 

## 1. Write function to allow specifying which schools (then embed in `grad_year_plots()` function)

## Consider making schools of interest a searchable text input in the shiny app:
##i.e.,:

#UI
`textInput(school_int, "School of Interest", value = "", width = NULL, placeholder = NULL)`

# Server
`school_of_interest <- reactive({input$school_int})`



```{r}
schools_of_interest <- 
  c(
  'Appling County High School', 
  'Bacon County High School',
  'Apalachee High School'
)
## basically this: filter(instn_name %in% schools_of_interest)
## with a warning embedded
```

## 2. Write a function to save the plots 

```{r}
# create file directory
files <- str_replace_all(tolower(unique(d0$instn_name)[1:100]), " ", "-")
paths <- here::here("Plots", glue("{files}.png"))
```

## 3. Make it interactive

* shiny to choose which plots to download
* `reactable` table to see the data
